Simulation

### 2023-10-31 simulation.qmd
Canonicalize Stan code
I don't think that's a word.

library(posterior)
library(mvtnorm)
library(ggdist)
library(brms)
library(tidyverse)

@@

>>>>

library(posterior)
library(mvtnorm)
library(cmdstanr)
library(ggdist)
library(brms)
library(tidyverse)

@@

Let us then compile and sample from the cmdstanr model

```{r}
fit <- cmdstanr::cmdstan_model("model-ar1.stan", compile = FALSE)
fit$format(
  canonicalize = list("deprecations"), 
  overwrite_file = TRUE, 
  backup = FALSE
)
```
